---
title: "S17 DV Final Project"
output:
  html_document:
    toc: yes
  html_notebook:
    toc: yes
authors: Christian Atayde, Jennifer Chung, Ryan Mak, Vivian Wang
---

#**Introduction**
For this project, we will be using two different data sets.
The first dataset (which will be our main dataset) is
The second dataset is 
In these two datasets, we will be comparing 

To download the data needed for this project:

1. Click or copy/paste this link to your web browser https://data.world/ryanmak/s-17-dv-final-project
2. Download the files "" and "".

The website we got our datasets was 

#**R Configuration**
Below we display our sessionInfo(). 

```{r}
sessionInfo(package=NULL)
```

#**ETL**

Here we have the ETL code to clean our datasets.

```{r}
source("../01 Data/ETL.OIS_Dataset_Incidents.R")
```

```{r}
source("../01 Data/ETL.OIS_Dataset_Officers.R")
```

```{r}
source("../01 Data/ETL.OIS_Dataset_Subjects.R")
```

#**Shiny**

This is the link to the Shiny Apps that was published for our project: 

```{r}'
source("../02 Shiny/server.R")
source("../02 Shiny/ui.R")
```


#**The Data**
